Fractional land cover classification method assessment using PROBA-V satellite data

### 2019-04-16 article/article.tex
Changes from papeeria
Add graphviz support
Include the graphics as static PDF (as Papeeria doesn't shell escape)
Addition of plots into the paper

% Custom packages
\usepackage[acronym,toc,shortcuts,nohypertypes=acronym]{glossaries}
\usepackage[colorlinks, allcolors=blue, unicode]{hyperref}
\usepackage{hyperxmp} % Import license metadata
\usepackage{titling} % Get the author for the metadata
\usepackage{textcomp} % \texttimes

@@

@@

@@

@@

\minisection{Author Contributions} Something

>>>>

% Custom packages
\usepackage[acronym,toc,shortcuts,nohypertypes=acronym]{glossaries}
\usepackage[colorlinks, allcolors=blue, unicode]{hyperref}
\usepackage{hyperxmp} % Import license metadata
\usepackage{titling} % Get the author for the metadata
\usepackage{textcomp} % \texttimes
%\usepackage[pdf]{graphviz} % Importing dot files; can be replaced with generated PDFs
\usepackage[norefs,nocites]{refcheck} % Develop: warn if figure is not referenced

@@

\begin{figure}
 %\inputdigraph[width=\textwidth]{article-figures/algorithms}{dot}
 \includegraphics[width=\textwidth]{article-figures/algorithms}
 \caption{Preprocessing chain.}
 \label{fig-preprocessing}
\end{figure}

@@

\subsection{Model tuning (multi-step approach) to account for value imbalance}

As the dataset is unbalanced (dominated by zeroes and hundreds) and thus the objective function tends to draw the model towards good prediction of 0/100, whereas in regression the middle is also important. Therefore we tried several approaches to increase the accuracy of the middle predictions.

We compared a single model of the best algorithm, to a two-step approach: one model to predict zeroes, and one model to predict non-zeroes; and a three-step approach, with one model to predict pixel purity (i.e. if we face a classification or a regression problem), one to perform regression (on mixed pixels) and one to perform classification (on pure pixels).

In addition, we investigated applying histogram matching, by matching the histogram of the predictions back to the histogram of the training set.

@@

% 1:1 plots
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/binplots/2019-04-12-rf-1m-uncor-points-a001s2}
    \caption{Random Forest single model prediction correspondence to ground truth (raw points with overplotting).}
    \label{raw-rf-1m-uncor}
\end{figure}
% Binplots
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/binplots/2019-04-12-rf-1m-uncor-point-n100s20}
    \caption{Random Forest single model prediction correspondence to ground truth, 100x100 bins.}
    \label{bin-rf-1m-uncor-n100}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/binplots/2019-04-12-rf-1m-uncor-point-n50s20sqrt}
    \caption{Random Forest single model prediction correspondence to ground truth, 50x50 bins, square root transformation.}
    \label{bin-rf-1m-uncor-n50sqrt}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/binplots/2019-04-12-rf-1m-uncor-point-n50s10sqrt}
    \caption{Random Forest single model prediction correspondence to ground truth, 50x50 bins, square root transformation, smaller circle sizes.}
    \label{bin-rf-1m-uncor-n50sqrts10}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/binplots/2019-04-12-rf-1m-uncor-raster-n50sqrt}
    \caption{Random Forest single model prediction correspondence to ground truth, square root transformation.}
    \label{bin-rf-1m-uncor-rastersqrt}
\end{figure}

% Hexplots
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/hexplots/2019-03-22-rf-1m-uncor-hex}
    \caption{Random Forest single model prediction correspondence to ground truth.}
    \label{hex-rf-1m-uncor}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/hexplots/2019-03-22-rf-3m-uncor-hex}
    \caption{Random Forest three-step model prediction correspondence to ground truth.}
    \label{hex-rf-3m-uncor}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/hexplots/2019-03-22-rf-1m-uncor-hm-hex}
    \caption{Random Forest single model prediction (histogram matched) correspondence to ground truth.}
    \label{hex-rf-1m-uncor-hm}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/hexplots/2019-03-22-rf-3m-uncor-hm-hex}
    \caption{Random Forest three-step model prediction (histogram matched) correspondence to ground truth.}
    \label{hex-rf-3m-uncor-hm}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/hexplots/2019-03-22-rf-3m-uncor-hma-hex}
    \caption{Random Forest three-step model prediction (histogram matched middle, proportionally) correspondence to ground truth.}
    \label{hex-rf-3m-uncor-hma}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/hexplots/2019-03-22-rf-3m-uncor-hmb-hex}
    \caption{Random Forest three-step model prediction (histogram matched non-extremes) correspondence to ground truth.}
    \label{hex-rf-3m-uncor-hmb}
\end{figure}

% Boxplots
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/boxplots/2019-03-19-rf-1m-uncor-box}
    \caption{Random Forest single model prediction correspondence to ground truth.}
    \label{box-rf-1m-uncor-hm}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/boxplots/2019-03-19-rf-2m-uncor-box}
    \caption{Random Forest two-step model prediction correspondence to ground truth.}
    \label{box-rf-2m-uncor-hm}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/boxplots/2019-03-19-rf-3m-uncor-box}
    \caption{Random Forest three-step model prediction correspondence to ground truth.}
    \label{box-rf-3m-uncor-hm}
\end{figure}

% Barplots
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/barplots/2019-03-19-rf-1m-uncor-bar}
    \caption{Random Forest single model prediction accuracies per class, per predicted magnitude (extremes vs middle)}
    \label{bar-rf-1m-uncor}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/barplots/2019-03-19-rf-2m-uncor-bar}
    \caption{Random Forest two-step model prediction accuracies per class, per predicted magnitude (extremes vs middle)}
    \label{bar-rf-2m-uncor}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/barplots/2019-03-19-rf-3m-uncor-bar}
    \caption{Random Forest three-step model prediction accuracies per class, per predicted magnitude (extremes vs middle)}
    \label{bar-rf-3m-uncor}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/barplots/2019-03-22-rf-1m-uncor-hm-bar}
    \caption{Random Forest single model prediction (histogram matched) accuracies per class, per predicted magnitude (extremes vs middle)}
    \label{bar-rf-1m-uncor-hm}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{article-figures/barplots/2019-03-22-rf-3m-uncor-hm-bar}
    \caption{Random Forest three-step model prediction (histogram matched) accuracies per class, per predicted magnitude (extremes vs middle)}
    \label{bar-rf-3m-uncor-hm}
\end{figure}

% Maps
\begin{figure}
    \includegraphics[width=\textwidth]{article-figures/maps/2019-03-26-rf-1m-bubble}
    \caption{Random Forest single model prediction residuals per class, spatially}
    \label{resid-rf-1m-uncor}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{article-figures/maps/2019-03-26-rf-3m-bubble}
    \caption{Random Forest three-step model prediction residuals per class, spatially}
    \label{resid-rf-3m-uncor}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{article-figures/maps/2019-04-10-rasterised-validation}
    \caption{Validation data spatially}
    \label{raster-validation}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{article-figures/maps/2019-04-10-rasterised-rf-1m-uncor}
    \caption{Random Forest single model predictions spatially}
    \label{raster-rf-1m-uncor}
\end{figure}

@@

\minisection{Author Contributions} DM JV NT MH ML
